CSCI 447: Project 1

### 2019-09-13 paper/paper.tex
updated abstract and over all goal

In this assignment, we implemented the naive Bayes machine learning algorithm [3] on 5 data sets. We utilized 10-fold cross-validation to test our implementation and measured accuracy with two loss functions: 0-1 Loss, and Precision/Recall [1].

@@

\section{Problem Statement}
Given a data set of which all the correct classifications are known, we can implement and execute a training algorithm on a subset of the data. Then, once trained, the algorithm will guess the classes of another subset of the data and measure the performance. For this assignment, we were provided with 5 real-world data sets. Our task was to implement a training algorithm and guess classifications for each of these 5 data sets and then utilize two different loss functions to measure the accuracy and performance of our predictions. We ran this algorithm on the original versions of each data set, and then introduced noise to each of the data sets by shuffling attribute values among 10\% of the values, and ran the algorithm of the five shuffled versions of the data. \\ \\
% Hypotheses
Our hypotheses for each data set are as follows: \\ \\
\textit{Breast Cancer Wisconsin:} This data set is comprised of 9 quantitative variables, and each data example can be classified as either benign or malignant. We hypothesized that, given that there are only two possible classifications, that we will achieve no less than 85\% accuracy (i.e. a 0-1 Loss score of 0.75) on our un-shuffled data. We think that the shuffled breast cancer data will be no more than 3\% less accurate. \\ \\
\textit{Glass:} This data set is comprised of 7 quantitative variables, and each data example can be classified as one of 7 possible glass types: building\_windows\_float\_processed, building\_windows\_non\_float\_processed, vehicle\_windows\_float\_processed, vehicle\_windows\_non- \\ \_float\_processed, containers, tableware, or headlamps. We hypothesize that we will achieve no less that 65\% accuracy (0-1 Loss of 0.65) for the un-shuffled data, given that there are 7 potential classes. The shuffled data, we predict, will be no more than 5\% less accurate than the shuffled data.\\ \\
\textit{Iris:} This data set is comprised of 4 quantitative variables. Each data example can be classified as one of three different flower types. We are predicting approximately 75\% (0-1 Loss of 0.75) accuracy. \\ \\
\textit{Soybean:} This data set is comprised of 35 attributes, and each data example can be classified as one of four different classifiers. We hypothesize 70\% accuracy (0-1 Loss of 0.7) for this un-shuffled data. For the shuffled data we are predicting the accuracy to be approximately 3\% less accurate.\\ \\
\textit{Voting Records:} This data set is comprised 16 categorical attributes, and each example may be classified as either republican or democrat. We are hypothesizing approximately 85\% accuracy (0-1 Loss of 0.85) for this dataset. We are predicting that the shuffled voting-record data should no more than 3\% less accurate than the shuffled data.\\

@@

\subsection{Shuffling/Applying Noise}
We implemented our prediction algorithm on the original version of each data set, and also introduced noise to each data set by randomly selecting 10\% of each data set and the shuffling attribute values. We then ran our algorithm on these shuffled versions of each data set.

@@

>>>>

In this assignment, we implemented the naive Bayes machine learning algorithm [3] on 5 data sets. We utilized 10-fold cross-validation to test our implementation and measured difference in accuracy between the average accuracy returned by the cross-validation of the original data set and the average accuracy returned by the cross-validation of the data set with 10\% noise applied, using two loss functions: 0-1 Loss, and Precision/Recall [1].

@@

\section{Problem Statement}
Given a data set of which all the correct classifications are known, we can implement and execute a training algorithm on a subset of the data. Then, once trained, the algorithm will guess the classes of another subset of the data and measure the performance. For this assignment, we were provided with 5 real-world data sets. Our task was to implement a training algorithm and guess classifications for each of these 5 data sets and then utilize two different loss functions to measure the accuracy and performance of our predictions. We ran this algorithm on the original versions of each data set, and then introduced noise to each of the data sets by shuffling attribute values among 10\% of the values, and ran the algorithm of the five shuffled versions of the data. So now we want to know how the noise introduced via shuffling will affect our accuracy. \\ \\
% Hypotheses
Our hypotheses for each data set are as follows: \\ \\
\textit{Breast Cancer Wisconsin:} This data set is comprised of 9 quantitative variables, and each data example can be classified as either benign or malignant. We hypothesized that, given that there are only two possible classifications, that we will achieve no less than 85\% accuracy (i.e. a 0-1 Loss score of 0.75) on our un-shuffled data. We think that the shuffled breast cancer data will be no more than 3\% less accurate. \\ \\
\textit{Glass:} This data set is comprised of 7 quantitative variables, and each data example can be classified as one of 7 possible glass types: building\_windows\_float\_processed, building\_windows\_non\_float\_processed, vehicle\_windows\_float\_processed, vehicle\_windows\_non- \\ \_float\_processed, containers, tableware, or headlamps. We hypothesize that we will achieve no less that 65\% accuracy (0-1 Loss of 0.65) for the un-shuffled data, given that there are 7 potential classes. The shuffled data, we predict, will be no more than 5\% less accurate than the shuffled data.\\ \\
\textit{Iris:} This data set is comprised of 4 quantitative variables. Each data example can be classified as one of three different flower types. We are predicting approximately 75\% (0-1 Loss of 0.75) accuracy. \\ \\
\textit{Soybean:} This data set is comprised of 35 attributes, and each data example can be classified as one of four different classifiers. We hypothesize 70\% accuracy (0-1 Loss of 0.7) for this un-shuffled data. For the shuffled data we are predicting the accuracy to be approximately 3\% less accurate.\\ \\
\textit{Voting Records:} This data set is comprised 16 categorical attributes, and each example may be classified as either republican or democrat. We are hypothesizing approximately 85\% accuracy (0-1 Loss of 0.85) for this dataset. We are predicting that the shuffled voting-record data should no more than 3\% less accurate than the shuffled data.\\

@@

@@

\subsection{Shuffling/Applying Noise}

In addition to implementing our prediction algorithm for the plain version of each data set, we also ran it with a 10\% noise modifier applied to the training data set in order to try and grasp how noise might affect the naive bayes machine learning algorithm.

We implemented our prediction algorithm on the original version of each data set, and also introduced noise to each data set by randomly selecting 10\% of each data set and the shuffling attribute values. We then ran our algorithm on these shuffled versions of each data set.
